\thesistitle

### 2019-07-20 sections/conclusion.tex
Partial block refactoring example

\subsubsection{Partial block}
We did not consider clones for refactoring that span a part of a block. Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.

\subsubsection{Overlap within a clone class}
We do not consider clone classes for refactoring that overlap in the clone class itself. That is because such clones might require other techniques to refactor them. We consider analyzing such refactoring methods future work.

@@

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
public boolean doStuff(){
  int numbers = 456;
|\highlightYellow|  if(doA());
|\highlightYellow|    return false;
|\highlightYellow|  doB();
  doC();
|\highlightYellow|  if(doA());
|\highlightYellow|    return false;
|\highlightYellow|  doB();
  return true;
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
public boolean doStuff(){
  int numbers = 456;
|\highlightYellow|  if(!doAandB())
|\highlightYellow|    return false;
  doC();
|\highlightYellow|  return doAandB();
}

public boolean doAandB(){
  if(doA())
    return false;
  doB(var2);
  return true;
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring a method that is obstructed by a complex control flow.}
\label{fig:complexcontrolflowrefactoring}
\end{figure}

>>>>

\subsubsection{Partial block}
We did not consider clones for refactoring that span a part of a block. Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable. For instance, if the programming language supports lambda expressions, we can move the difference of statements in the block in a lambda expression. Figure \ref{fig:partialblockrefactoring} shows an example of such a refactoring opportunity.

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
public void doStuff(){
|\highlightYellow|  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
    System.out.println("hello!");
  }
|\highlightYellow|  for(int i = 0; i<5; i++) {
    CoreController.activateCore(i);
  }
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
public void doStuff(){
|\highlightYellow|  doFiveTimes(() -> System.out.println("hello!"));
|\highlightYellow|  doFiveTimes(() -> CoreController.activateCore(i));
}

public void doFiveTimes(Runnable runnable){
  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
    runnable.run();
  }
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring a method that is obstructed by a complex control flow.}
\label{fig:partialblockrefactoring}
\end{figure}

\subsubsection{Overlap within a clone class}
We do not consider clone classes for refactoring that overlap in the clone class itself. That is because such clones might require other techniques to refactor them. We consider analyzing such refactoring methods future work. An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}. In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}. To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
public void sayHello(){
|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
public void sayHello(){
|\highlightYellow|  for(int i = 0; i<5; i++){
|\highlightYellow|    System.out.println("hello!");
|\highlightYellow|  }
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring a clone class that has overlap between clone instances.}
\label{fig:overlaprefactoring}
\end{figure}

@@

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
public boolean doStuff(){
|\highlightYellow|  if(doA());
|\highlightYellow|    return false;
|\highlightYellow|  doB();
  doC();
|\highlightYellow|  if(doA());
|\highlightYellow|    return false;
|\highlightYellow|  doB();
  return true;
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
public boolean doStuff(){
|\highlightYellow|  if(!doAandB())
|\highlightYellow|    return false;
  doC();
|\highlightYellow|  return doAandB();
}

public boolean doAandB(){
  if(doA())
    return false;
  doB();
  return true;
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring a method that is obstructed by a complex control flow.}
\label{fig:complexcontrolflowrefactoring}
\end{figure}
